\begin{hangparas}{2em}{1}
Arsalan, M., \& Niraj, J. (2016). A Comprehensive Study of Security of Internet-of-Things. \textit{IEEE Transactions on Emerging Topics in Computing, 5(4).}

Braue, D. (2018, September 7). Users’ poor home IoT security could become your next headache. Retrieved October 29, 2018, from \url{https://www.cso.com.au/article/646392/users-poor-home-iot-security-could-become-your-next-headache/}

Burgess, M. (2018, February 16). What is the Internet of Things? WIRED explains. \textit{Wired UK.} Retrieved from \url{https://www.wired.co.uk/article/internet-of-things-what-is-explained-iot}

Cagnazzo, M. (n.d.). Using the Strava Heatmap to Identify and Track Military Personnel – Matteo Cagnazzo. Retrieved November 4, 2018, from \url{https://www.cagnazzo.de/using-stravas-heatmap-to-identify-and-track-military-personnel/}

California Consumer Privacy Act. Retrieved December 7, 2018, from \url{https://www.caprivacy.org/}

Code of Practice for Consumer IoT Security (October 2018). Retrieved December 7, 2018, from \url{https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/747413/Code_of_Practice_for_Consumer_IoT_Security_October_2018.pdfhttps://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/747413/Code_of_Practice_for_Consumer_IoT_Security_October_2018.pdf}

“Computer Security Is Broken from Top to Bottom.” \textit{The Economist}, 8 Apr. 2017, \url{www.economist.com/science-and-technology/2017/04/08/computer-security-is-broken-from-top-to-bottom}. 

Dataguise. (2017, February 15). Data Minimization in the GDPR: A Primer. Retrieved November 7, 2018, from \url{https://www.dataguise.com/gdpr-compliance-data-minimization-use-purpose/}

Desai, D., \& Upadhyay, H. (2014). Security and Privacy Consideration for Internet of Things in Smart Home Environments, 11.

Developments on NIS Directive in EU Member States (15 June 2018). Retrieved December 7, 2018, from \url{https://www.unibw.de/code-events/material-bilder/workshops/ws4_recht-regulierung_vortrag_duisberg_02.pdf}

Elahi, A., \& Gschwender, A. (2009). Introduction to the Zigbee Wireless Sensor and Control Network: Zigbee Device Types. Retrieved from \url{http://www.informit.com/articles/article.aspx?p=1409785\&seqNum=3}

Enright, K. (2018, September 24). Proposing a framework for data protection legislation. Retrieved November 7, 2018, from \url{https://www.blog.google/outreach-initiatives/public-policy/proposing-framework-data-protection-legislation/}

EU GDPR. (n.d.). GDPR FAQs – EUGDPR. Retrieved November 7, 2018, from \url{https://eugdpr.org/the-regulation/gdpr-faqs/}

Get To Know The Four Types Of Data In The Internet Of Things. (2015, August 13). Retrieved November 3, 2018, from \url{https://readwrite.com/2015/08/13/five-types-data-internet-of-things/}

Gope, P., \& Sikdar, B. (2018). Lightweight and Privacy-Preserving Two-Factor Authentication Scheme for IoT Devices. \textit{IEEE Internet of Things Journal}.

Heartfield, R., Loukas, G., Budimir, S., Bezemskij, A., Fontaine, J. R. J., Filippoupolitis, A., \& Roesch, E. (2018). A taxonomy of cyber-physical threats and impact in the smart home. \textit{Computers \& Security}, 78, 398–428. \url{https://doi.org/10.1016/j.cose.2018.07.011}

Hern, A. (n.d.). Strava suggests military users “opt out” of heatmap as row deepens. Retrieved November 4, 2018, from \url{https://www.theguardian.com/technology/2018/jan/29/strava-secret-army-base-locations-heatmap-public-users-military-ban}

Hunt, T. (2013, December 4). Introducing “Have I been pwned?” – aggregating accounts across website breaches. Retrieved November 5, 2018, from \url{https://www.troyhunt.com/introducing-have-i-been-pwned/}

Internet of Things (IoT) Cybersecurity Improvement Act of 2017. Retrieved December 7, 2018, from https://www.congress.gov/bill/115th-congress/senate-bill/1691

IOT Consumer TIPS Act of 2017. Retrieved December 7, 2018, from \url{https://www.congress.gov/bill/115th-congress/senate-bill/2234}

i-scoop. (n.d.-a). Data portability under the GDPR: the right to data portability explained. Retrieved November 7, 2018, from \url{https://www.i-scoop.eu/gdpr/right-to-data-portability/}

i-scoop. (n.d.-b). The right to erasure or right to be forgotten under the GDPR explained. Retrieved November 6, 2018, from \url{https://www.i-scoop.eu/gdpr/right-erasure-right-forgotten-gdpr/}

IT Governance UK. (n.d.). GDPR - Data Protection Impact Assessment (DPIA) | IT Governance UK. Retrieved November 7, 2018, from \url{https://www.itgovernance.co.uk/privacy-impact-assessment-pia}

Lin, H., Bergmann, N., Lin, H., \& Bergmann, N. W. (2016). IoT Privacy and Security Challenges for Smart Home Environments. \textit{Information}, 7(3), 44. \url{https://doi.org/10.3390/info7030044}

Lynggaard, P., \& Skouby, K. E. (2016). Complex IoT Systems as Enablers for Smart Homes in a Smart City Vision. \textit{Sensors (Basel, Switzerland)}, 16(11). \url{https://doi.org/10.3390/s16111840}

Mordorintelligence. (2018). \textit{Smart Homes Market Size, Share - Segmented by Product Type (Security \& Surveillance Systems, Lighting Systems, HVAC\&R Controls) and Region - Growth, Trends and Forecasts (2018 - 2023)}.

Network Specifications. (2014, August 13). Retrieved November 5, 2018, from \url{https://www.zigbee.org/zigbee-for-developers/network-specifications/}

O’Haver, L. (2016, December 8). Fail Closed, Fail Open, Fail Safe and Failover: ABCs of Network Visibility | Ixia. Retrieved November 6, 2018, from \url{https://www.ixiacom.com/company/blog/fail-closed-fail-open-fail-safe-and-failover-abcs-network-visibility}

Pwned Passwords in Practice: Real World Examples of Blocking the Worst Passwords. (2018, May 29). Retrieved November 6, 2018, from \url{https://www.troyhunt.com/pwned-passwords-in-practice-real-world-examples-of-blocking-the-worst-passwords/}

Ren, Z., Liu, X., Ye, R., \& Zhang, T. (2017). Security and privacy on internet of things. Presented at the 2017 7th IEEE International Conference on Electronics Information and Emergency Communication (ICEIEC), IEEE.

Rouffineau, T. (2016, December 15). Research: Consumers are terrible at updating their connected devices. Retrieved November 7, 2018, from \url{/2016/12/15/research-consumers-are-terrible-at-updating-their-connected-devices}

Rudresh, V. (2017, November 1). Zigbee Security: Basics (Part 1). Retrieved November 6, 2018, from \url{https://research.kudelskisecurity.com/2017/11/01/zigbee-security-basics-part-1/}

Schneier, B. (2018). \textit{Click Here to Kill Everybody: Security and Survival in a Hyper-connected World}. W. W. Norton \& Company.

Soltan, S., \& Mittal, P. (n.d.). BlackIoT: IoT Botnet of High Wattage Devices Can Disrupt the Power Grid, 19.

Spiegel, S. (2014, May 20). Europe: 1, Google: 0: EU Court Ruling a Victory for Privacy. \textit{Spiegel Online}. Retrieved from \url{http://www.spiegel.de/international/business/court-imposes-right-to-be-forgotten-on-google-search-results-a-970419.html}

Stevel. (2018, January 29). Advanced Deanonymization through Strava. Retrieved November 4, 2018, from \url{http://steveloughran.blogspot.com/2018/01/advanced-denanonymization-through-strava.html}

Strategic Principles for Securing the Internet of Things (IoT). (2016, November 15). US Department of Homeland Security.

The Zigbee Alliance Celebrates 15 Years and A Decade of Standards. (2017, October 9). Retrieved November 5, 2018, from \url{https://www.zigbee.org/the-zigbee-alliance-celebrates-15-years-and-a-decade-of-standards/}

UK ICO. (2018, August 6). Data protection impact assessments. Retrieved November 7, 2018, from \url{https://ico.org.uk/for-organisations/guide-to-the-general-data-protection-regulation-gdpr/accountability-and-governance/data-protection-impact-assessments/}

Waldron, S. (2017). Experts Call for International Collaboration on Cybersecurity Issues. Retrieved November 7, 2018, from \url{https://www.aaas.org/news/experts-call-international-collaboration-cybersecurity-issues}

Warren, S., \& Brandeis, L. (1890). The Right to Privacy. \textit{Harvard Law Review, IV(5)}. Retrieved from \url{http://groups.csail.mit.edu/mac/classes/6.805/articles/privacy/Privacy_brand_warr2.html}

Woodie, A. (2016). The Growing Menace of Data Hoarding. Retrieved November 7, 2018, from \url{https://www.datanami.com/2016/06/13/growing-menace-data-hoarding/}

zeb. (2017, November 14). GDPR deep dive—how to implement the ‘right to be forgotten.’ Retrieved November 7, 2018, from \url{https://www.bankinghub.eu/banking/finance-risk/gdpr-deep-dive-implement-right-forgotten}

Ziegeldorf, J. H., Morchon, O. G., \& Wehrle, K. (2014). Privacy in the Internet of Things: threats and challenges: Privacy in the Internet of Things: threats and challenges. \textit{Security and Communication Networks, 7(12)}, 2728–2742. \url{https://doi.org/10.1002/sec.795}

Zigbee Leads the Wireless Mesh Sensor Network Market. (2018, August 10). Retrieved November 5, 2018, from \url{https://www.zigbee.org/zigbee-leads-the-wireless-mesh-sensor-network-market/}
\end{hangparas}
